---
title: "Community assets and capacity mapping."
author: "Prepared by UNHCR Egypt"
date: "Cairo, generated on the `r format(Sys.Date(),  '%d %B %Y')`"
output:
  word_document:
    fig_caption: yes
    fig_height: 8
    fig_width: 15
    toc: yes
    toc_depth: 2
    reference_docx: style-unhcr-portrait.docx
---

<!-- To run in console -->
<!-- install.packages("rmarkdown", repos="http://cran.us.r-project.org") -->
<!-- library(rmarkdown) -->
<!-- rmarkdown::render('code/3-report.Rmd')  -->
```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
mainDir <- getwd()
mainDirroot <- substring(mainDir, 0 , nchar(mainDir)- 5)
## Load all required packages
source(paste0(mainDirroot,"/code/0-theme.R"))
source(paste0(mainDirroot,"/code/0-packages.R"))
library(koboloadeR)
## Provide below the name of the form in xsl form - format should be xls not xlsx
form <- "form.xls"
dico <- read.csv(paste0(mainDirroot,"/data/dico_",form,".csv"), encoding="UTF-8", na.strings="")
data.or <- read.csv(paste0(mainDirroot,"/data/data.csv"), encoding="UTF-8", na.strings="NA")

## label Variables
data <- kobo_label(data.or , dico)


```

#  1) Data load

#  2) Introductory questions (to be filled by surveyor)

##  2.1) Status of surveyor

```{r p.statussurveyor, echo=FALSE, fig.height=8, fig.width=15}
plot (p.statussurveyor)
```

##  2.2) Country where mapping takes place

```{r p.mapcountry, echo=FALSE, fig.height=8, fig.width=15}
plot (p.mapcountry)
```

##  2.3) Governorate/District where mapping takes place

```{r p.mapgovernorate, echo=FALSE, fig.height=8, fig.width=15}
plot (p.mapgovernorate)
```

##  2.4) City where mapping takes place

```{r p.mapcity, echo=FALSE, fig.height=8, fig.width=15}
plot (p.mapcity)
```

##  2.5) Type of collaborating community in this mapping

```{r p.collabunit, echo=FALSE, fig.height=8, fig.width=15}
plot (p.collabunit)
```

##  2.6) List of collaborating entities (for internal use only)

```{r p.unitslist, echo=FALSE, fig.height=8, fig.width=15}
plot (p.unitslist)
```


#  3) Community demographics & structure
##  3.1) Community type (formal/informal/individual)

```{r p.commtype, echo=FALSE, fig.height=8, fig.width=15}
plot (p.commtype)
```

##  3.2) Demographics of communities (informal & formal)

##  3.2.1) Way of establishment

```{r p.establishment, echo=FALSE, fig.height=8, fig.width=15}
plot (p.establishment)
```

##  3.2.2) Community structure

```{r p.structure, echo=FALSE, fig.height=8, fig.width=15}
plot (p.structure)
```

##  3.2.3) Membership requirements

```{r p.membership, echo=FALSE, fig.height=8, fig.width=15}
plot (p.membership)
```

##  3.2.4) Members

```{r p.members, echo=FALSE, fig.height=8, fig.width=15}
plot (p.members)
```

##  3.2.5) Community size

```{r p.size, echo=FALSE, fig.height=8, fig.width=15}
plot (p.size)
```

##  3.2.6) Proportion of female, elderly, children within the community

```{r p.dependencies, echo=FALSE, fig.height=8, fig.width=15}
plot (p.dependencies)
```

##  3.2.7) Ethical standards in the community

```{r p.ethics, echo=FALSE, fig.height=8, fig.width=15}
plot (p.ethics)
```

##  3.3) Demographics of engaged individuals

##  3.3.1) Sex

```{r p.indsex, echo=FALSE, fig.height=8, fig.width=15}
plot (p.indsex)
```

##  3.3.2) Age*


##  3.3.3) Nationality

```{r p.indnationality, echo=FALSE, fig.height=8, fig.width=15}
plot (p.indnationality)
```


#  4) Community work & services
##  4.1) Working area

```{r p.workarea, echo=FALSE, fig.height=8, fig.width=15}
plot (p.workarea)
```

##       Prioritized working area

```{r p.workarea.prio, echo=FALSE, fig.height=8, fig.width=15}
plot (p.workarea.prio)
```

##  4.2) Community services

```{r p.services, echo=FALSE, fig.height=8, fig.width=15}
plot (p.services)
```

##       Prioritized community services

```{r p.services.prio, echo=FALSE, fig.height=8, fig.width=15}
plot (p.services.prio)
```

##  4.3) Recognition of engaged individual (entity = individual) within the community

```{r p.indrecognition, echo=FALSE, fig.height=8, fig.width=15}
plot (p.indrecognition)
```

##  4.4) Skills of enganged individual (entity = individual)

```{r p.indskills, echo=FALSE, fig.height=8, fig.width=15}
plot (p.indskills)
```

##  4.5) Talents of enganged individual (entity = individual)

```{r p.indtalents, echo=FALSE, fig.height=8, fig.width=15}
plot (p.indtalents)
```


#  5) Referrals*

#  6) Targeted groups
##  6.1) Percent of targeted groups

```{r p.poc, echo=FALSE, fig.height=8, fig.width=15}
plot (p.poc)
```

##  6.2) Specific groups of concern

```{r p.specific, echo=FALSE, fig.height=8, fig.width=15}
plot (p.specific)
```


#  7) Active community members
##  7.1) Type of active community members

```{r p.actmembers, echo=FALSE, fig.height=8, fig.width=15}
plot (p.actmembers)
```

##  7.2) Duration of community work

```{r p.duration, echo=FALSE, fig.height=8, fig.width=15}
plot (p.duration)
```


#  8) Communication channels
##  8.1) Type of used communication shannels

```{r p.channels, echo=FALSE, fig.height=8, fig.width=15}
plot (p.channels)
```

##  8.2) List of manual entries of specific communication channels

```{r p.addresses, echo=FALSE, fig.height=8, fig.width=15}
plot (p.addresses)
```

#  9) Meeting space
##  9.1) Type of meeting space

```{r p.meetingspace, echo=FALSE, fig.height=8, fig.width=15}
plot (p.meetingspace)
```


##  9.2) Type of access to meeting space

```{r p.access, echo=FALSE, fig.height=8, fig.width=15}
plot (p.access)
```

##  9.3) Conduciveness of meeting space

```{r p.conduciveness, echo=FALSE, fig.height=8, fig.width=15}
plot (p.conduciveness)
```


# 10) Community challenges

```{r p.challenges, echo=FALSE, fig.height=8, fig.width=15}
plot (p.challenges)
```


# 11) Community collaboration
## 11.1) Reward to motivate community work

```{r p.reward, echo=FALSE, fig.height=8, fig.width=15}
plot (p.reward)
```

## 11.2) Collaboration with UNHCR

```{r p.collabunhcr, echo=FALSE, fig.height=8, fig.width=15}
plot (p.collabunhcr)
```


# 12) Contact details (for internal use only)

```{r p.contact, echo=FALSE, fig.height=8, fig.width=15}
plot (p.contact)
```
